---
title: "Asset Class Allocation with Minimum-Variance Frontier Model"
author: "Glen Wang"
date: "8/4/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Install and active packages
```{r eval=FALSE}
install.packages("devtools")
library(devtools)
install.packages("IntroCompFinR", repos="http://R-Forge.R-project.org")
install_github("glenwang/R_MVFPortfolio/tree/master/MVFPortfolio")

```{r message=F, warning=F}
library(IntroCompFinR)
library(MVFPortfolio)
```

Select date range and securities. Then fetch adjusted price data from Yahoo Finance. 
```{r message=F, warning=F}
begindate = "2016-07-12"
sourc ="yahoo"
assetClassSymbols =c('VTI','VO','VB','SHY','BND', 'TLT', 'TIP','MUB','VEU','VSS','VWO','VNQ','DBC','GLD')
assetClassPriceData = AdjustedPrice(assetClassSymbols, begindate, sourc)
```

```{r}
head(assetClassPriceData)
tail(assetClassPriceData)
```
Create tables of return, risk, correlation and covariance. 
```{r message=F, warning=F}
assetClassReturnRiskTable = AnnualReturnRisk(assetClassPriceData)
head(assetClassReturnRiskTable)
assetClassReturnRiskCorrelationTable = RSTDCorr(assetClassPriceData)
head(assetClassReturnRiskCorrelationTable)
asssetClassCovarianceMatrixTable =CovMatrix(assetClassPriceData)
head(asssetClassCovarianceMatrixTable)
```

For each specified target return, create the asset classes' weights table and chart. Then draw each portfolio in the efficient frontier plot. 
```{r message=F, warning=F}
TargetReturn = c(.001, .003, .005, .007, .01, .03, .05, .07, .1, .11)
riskfree= .0293
assetClassReturnRiskWeightsTable = RSTDWtable(assetClassPriceData, TargetReturn, riskfree)
assetClasssEfficientFrontierPlot = efplot(assetClassReturnRiskWeightsTable)
```

